A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}). History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

\citet{Jafarpour_2009} compares KLT to discrete cosine transform (DCT) and goes on to state that the DCT is computationally more efficient than the KLT while being almost as accurate. \citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible. Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.

>>>>

A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}). History matching is the process of building or adjusting one or more sets of reservoir configurations (or realisations), such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}. It is important to note that reservoir configurations could be either a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

\citet{Jafarpour_2009} compares KLT and discrete cosine transform (DCT) and concluded that the DCT is computationally more efficient than the KLT while being almost as accurate. \citet{Tavakoli_2010} noted that history matching calculation of sensitivities for all production data with respect to system parameters (\ie{variables}) is not feasible. Hence, they (\citet{Tavakoli_2010}) explored a new parameterization for reducing the number of variables based on the principal right singular vectors of the dimensionless sensitivity matix.
